---
title: "Semantic Colour Analysis"
output: rmarkdown::github_document
---

## List of Functions:

* top_RGB_graph: Top Words, Analayze RGB, Plot Frequency
* top_RGB_data: Top Words, Analayze RGB, Plot Dataframe

* word_RGB_graph: Query Word, Analyze RGB, Plot Bar Graph
* word_RGB_data: Query Word, Analyze RGB, Plot Dataframe

* word_lum_graph: Query Word, Analyze Lum, Plot Bar Graph
* word_lum_data: Query Word, Analyze Lum, Plot Dataframe
* word_lum_RGB_scatter_smooth: Query Word, Analyze Lum, Plot Scatter w Smooth
* word_lum_RGB_scatter_data: Query Word, Analyze Lum, Plot Dataframe

* word_temp_RGB_scatter: Query Word, Analyze Temp, Plot Scatter
* word_temp_RGB_scatter_smooth: Query Word, Analyze Temp, Plot Scatter w Smooth
* word_temp_RGB_scatter_data: Query Word, Analyze Temp, Plot Dataframe


Clear 
```{r}
rm(list = ls())
```

Create Library
```{r message=FALSE, warning=FALSE}
library(devtools)

#install_github("detsutut/chroma", subdir="chromaR")

library(subtools) #subtitles manipulation
library(chromaR) #chromatic package
library(tidytext) 
library(chroma)
library(hms)
library(tidyverse)
library(ggplot2)
library(data.table)
library(dplyr)
library(stringr)
library(reshape2)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(magrittr)
library(readtext)
library(stringi)
library(quanteda)
library(SnowballC)
library(stopwords)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(tidytext)
library(rio)
library(tm)
library(knitr)
library(reshape)
```

# Cleaning

## 1 Define Parameters and Files
```{r}
moviename = "Fight Club (1999)"

movielistframes = getFrames("frames/Fight.Club.10th.Anniversary.Edition.1999.720p.BrRip.x264.YIFY.mp4.csv")
subs = data.frame(read_subtitles("subtitles/Fight.Club.10th.Anniversary.Edition.1999.720p.BrRip.x264.YIFY.srt"))

framerate = 23.98
```


## 2.1 Process Frames 

### 2.1.1 (for subs) Write Function to average colours within on Timeframe

```{r}
#Retrieve Movie Frames
movieframes_df = data.frame(movielistframes)
#add seconds parameter
movieframes_df = movieframes_df %>% mutate(s = frameId/framerate)

## Function
GetColorFromDialogue = function(movie_df,start_hms,end_hms){
  start_s = as.numeric(start_hms)
  end_s = as.numeric(end_hms)
  newframe_df = movieframes_df %>% 
    filter( s <= end_s & s >= start_s) %>%
    summarise_if(is.numeric, mean) %>%
    mutate(hexRGB = rgb(R,G,B, maxColorValue = 255)) %>%
    select(R,G,B,lum,hexRGB)
  return(newframe_df)
}
```

##2.2 Process Subs

### 2.2.1 Check which Dialogues are Advert and Remove
```{r}
print(head(subs))

#1 means dialogue 1 is removed
subs1 = subs[-c(1), ] 
```

### 2.2.2 Recheck List
```{r}
print(head(subs1))
```


### 2.2.3 Get Subtitles Data Frame and Insert Average Chromatic 
```{r message=FALSE, warning=FALSE}
#change col names
subs2 = subs1 %>% mutate(origin_text = Text_content)
colnames(subs2) = c("Dialogue_ID","Timecode_in","Timecode_out","text","origin_text")


#add additional Chromatic Data for Dialogue
subs3 = subs2
subs3$R = subs3$G = subs3$B = subs3$lum = subs3$hexRGB = NA
subs3$R[1861]

for (i in 1:nrow(subs3)){
  info_df = GetColorFromDialogue(movieframes_df,subs3$Timecode_in[i],subs3$Timecode_out[i])
  #insert RGB data
  subs3$R[i] = info_df$R
  subs3$G[i] = info_df$G
  subs3$B[i] = info_df$B
  subs3$lum[i] = info_df$lum
  subs3$hexRGB[i] = info_df$hexRGB
}

#tokenize into words instead
subs_word = unnest_tokens(subs3,word,text)

#clean tokens
data(stop_words)
subs_word_clean = subs_word %>% anti_join(stop_words) %>% 
  filter(!grepl('[1234567890]', word)) %>%
  filter(!grepl('<U+813F>', word)) %>% 
  add_count(word) %>% 
  arrange(desc(n))

#add word count and arrange by count
#subs_word_clean 
```

Show Text Frequency
```{r}
#Check instances
wordcount = subs_word_clean[,c(10,11)] %>%
  distinct %>% # average the colours 
  arrange(desc(n)) %>% 
  filter(n > 5)  #CUT OFF FOR OCCURANCE

#wordcount
```







# Analysis


## 0 Top Words Analysis

Top 20 Most Frequent Word
```{r}

top_RGB_graph = function(subs_word_clean,top_words,upperbound,lowerbound,correction,flip){
  
  #filter RGB
  subs_df = subs_word_clean[,c(6:11)] 
  
  #average RGB values
  avg_subs_df = subs_df %>% 
    group_by(word) %>%
    mutate_each(funs(mean)) %>%  
    distinct %>% # average the colours 
    arrange(desc(n)) %>% 
    mutate(hexRGB = rgb(R,G,B,maxColorValue = 255)) %>%  #add hexRGB
    filter(n > 1)  #remove singular instance
  
  df = avg_subs_df %>% filter (n>=lowerbound && n<=upperbound) %>%.[1:top_words,]
  df$vividRGB = vividHex(df$hexRGB,c(correction))

  positions = df$word
  p<-ggplot(df, aes(x=reorder(word,-n), y=n, fill=word)) +
    geom_bar(stat="identity") + scale_x_discrete(limits = positions)
  
  if (flip == "Y"){
    return( p + ggtitle(paste("Top ",top_words," Words",sep=""),paste(lowerbound," <= n <= ",upperbound,sep="") ) + scale_fill_manual(values = df$vividRGB) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(legend.position = "none") + coord_flip() )
  }
  else{
    return( p + ggtitle(paste("Top ",top_words," Words",sep=""),paste(lowerbound," <= n <= ",upperbound,sep="") ) + scale_fill_manual(values = df$vividRGB) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + theme(legend.position = "none"))
    
  }
  
}
  
top_RGB_data = function(subs_word_clean,top_words,upperbound,lowerbound,correction){
  
  #filter RGB
  subs_df = subs_word_clean[,c(6:11)] 
  
  #average RGB values
  avg_subs_df = subs_df %>% 
    group_by(word) %>%
    mutate_each(funs(mean)) %>%  
    distinct %>% # average the colours 
    arrange(desc(n)) %>% 
    mutate(hexRGB = rgb(R,G,B,maxColorValue = 255)) %>%  #add hexRGB
    filter(n > 1)  #remove singular instance
  
  df = avg_subs_df %>% filter (n>=lowerbound && n<=upperbound) %>%.[1:top_words,]
  df$vividRGB = vividHex(df$hexRGB,c(correction))

  return(df)
}


```

Sample Run
```{r warning=FALSE}
top_RGB_graph(subs_word_clean, top_words = 20, upperbound = 999, lowerbound = 0, correction = 'medium', flip = 'N')
head(top_RGB_data(subs_word_clean, top_words = 20, upperbound = 999, lowerbound = 0, correction = 'medium'))
```





## 1 word_RGB_graph [BAR GRAPH]
```{r}
##EXECUTE GRAPH

word_RGB_graph = function(subs_word_clean,query,choice,correction,flip){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  #graph
  if (choice == "Time") {
    
    #plot time graph
    p<-ggplot(w_df, aes(x=reorder(Time,-h), y = h, fill = Time))  +
      geom_bar(stat="identity")
    
    if (flip=="Y"){
      return(p + ggtitle("Word Query, RGB",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1], "  |  cor = ", correction, sep="")) + scale_fill_manual(values = simpl_df$vividRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip() )
    }
    else{
      return(p + ggtitle("Word Query, RGB",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1], "  |  cor = ", correction, sep="")) + scale_fill_manual(values = simpl_df$vividRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))
    }
    
  }
  if (choice == "ID") {
     #plot ID graph
    p<-ggplot(w_df, aes(x=reorder(Dialogue_ID,-h), y = h, fill = Dialogue_ID))  +
      geom_bar(stat="identity")
    
    if (flip=="Y"){
      return(p + ggtitle("Word Query, RGB",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1], "  |  cor = ", correction, sep="")) + scale_fill_manual(values = simpl_df$vividRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip() )
    }
    else{
      return(p + ggtitle("Word Query, RGB",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1], "  |  cor = ", correction, sep="")) + scale_fill_manual(values = simpl_df$vividRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))
    }
  }
}

##EXECUTE DATAFRAME

word_RGB_data = function(subs_word_clean,query,choice,correction){
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  
  
  #for color matching
  simpl_df = w_df  %>% distinct
  #print dialogue data
  data.frame(simpl_df$Time,simpl_df$Dialogue_ID,simpl_df$origin_text,simpl_df$vividRGB,simpl_df$hexRGB)
}
```

Sample Test
```{r}
#df, query, choice(Time/ID), correction (ultra/strong/medium/light), flip (Y/N)
word_RGB_graph(subs_word_clean, query = "jack's",choice = "Time", correction = "light", flip = "N") 
head(word_RGB_data(subs_word_clean, query = "jack's",choice = "Time", correction = "light") )

word_RGB_graph(subs_word_clean, query = "mayhem",choice = "Time", correction = "medium", flip = "N") 
head(word_RGB_data(subs_word_clean, query = "mayhem",choice = "Time", correction = "medium") )
word_RGB_graph(subs_word_clean, query = "pain",choice = "Time", correction = "light", flip = "N") 
head(word_RGB_data(subs_word_clean, query = "pain",choice = "Time", correction = "light") )
```

## 2 word_LUM_graph [BAR GRAPH]

```{r}
##EXECUTE GRAPH

word_lum_graph = function(subs_word_clean,query,choice,flip){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df = w_df %>% mutate(lumRGB = hsl(h=0,s=0,l= lum/120))
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  #graph
  if (choice == "Time") {
    
    #plot time graph
    p<-ggplot(w_df, aes(x=reorder(Time,-h), y = h, fill = Time))  +
      geom_bar(stat="identity")
    
    if (flip=="Y"){
      return(p + ggtitle("Word Query, Lum",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1], sep="")) + scale_fill_manual(values = simpl_df$lumRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip() )
    }
    else{
      return(p + ggtitle("Word Query, Lum",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , sep="")) + scale_fill_manual(values = simpl_df$lumRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))
    }
    
  }
  if (choice == "ID") {
     #plot ID graph
    p<-ggplot(w_df, aes(x=reorder(Dialogue_ID,-h), y = h, fill = Dialogue_ID))  +
      geom_bar(stat="identity")
    
    if (flip=="Y"){
      return(p + ggtitle("Word Query, Lum",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , sep="")) + scale_fill_manual(values = simpl_df$lumRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip() )
    }
    else{
      return(p + ggtitle("Word Query, Lum",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , sep="")) + scale_fill_manual(values = simpl_df$lumRGB) + theme(legend.position = "none") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)))
    }
  }
}

##EXECUTE DATAFRAME

word_lum_data = function(subs_word_clean,query,choice){
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df = w_df %>% mutate(lumRGB = hsl(h=0,s=0,l= lum/120))
  
  
  #for color matching
  simpl_df = w_df  %>% distinct
  #print dialogue data
  data.frame(simpl_df$Time,simpl_df$Dialogue_ID,simpl_df$origin_text,simpl_df$lum,simpl_df$lumRGB)
}
```

Sample Test
```{r}
word_lum_graph(subs_word_clean, query = "tyler",choice = "Time",  flip = "N") 
head(word_lum_data(subs_word_clean, query = "tyler",choice = "Time"))

word_RGB_graph(subs_word_clean, query = "tyler",choice = "Time", correction = "medium", flip = "N") 
head(word_RGB_data(subs_word_clean, query = "tyler",choice = "Time", correction = "medium"))
```

## 3 word_LUM_ [Scatter] 

```{r}
##EXECUTE GRAPH

word_lum_RGB_scatter = function(subs_word_clean,query,choice,correction,size){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  w_df = w_df %>% mutate(lumRGB = hsl(h=0,s=0,l= lum/120))
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  #graph
  if (choice == "Time") {
    p <- ggplot(w_df, aes(x=Timecode_in, y = lum, color = Time))  +
      geom_point(size = size)
    return(p  + ggtitle("Word Query, Lum/RGB Scatter",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none")
      )
    
  }
  if (choice == "ID") {
    p <- ggplot(w_df, aes(x=as.numeric(Dialogue_ID), y = lum, color = Dialogue_ID))  +
      geom_point(size = size) 
    return(p  + ggtitle("Word Query, Lum/RGB Scatter",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none"))
  }
}

##EXECUTE GRAPH

word_lum_RGB_scatter_smooth = function(subs_word_clean,query,choice,correction,size,span){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  w_df = w_df %>% mutate(lumRGB = hsl(h=0,s=0,l= lum/120))
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  
  #graph
  if (choice == "Time") {
    p <- ggplot(w_df, aes(x=Timecode_in, y = lum))  +
      geom_point(size = size) + geom_smooth(method = "loess",formula = 'y ~ x',color = "red",se = F , span = span)
    return(p  + ggtitle("Word Query, Lum/RGB Scatter Geom_Smooth",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none")
      )
    
  }
  if (choice == "ID") {
    p <- ggplot(w_df, aes(x=as.numeric(Dialogue_ID), y = lum))  +
      geom_point(size = size) + geom_smooth(method = "loess",formula = 'y ~ x',color = "red",se = F ,span = span)
    return(p  + ggtitle("Word Query, Lum/RGB Scatter Geom_Smooth",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction,sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none"))
  }
}


##EXECUTE DATAFRAME

word_lum_RGB_scatter_data = function(subs_word_clean,query,choice){
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c("light"))
  w_df = w_df %>% mutate(lumRGB = hsl(h=0,s=0,l= lum/120))
  
  
  #for color matching
  simpl_df = w_df  %>% distinct
  #print dialogue data
  data.frame(simpl_df$Time,simpl_df$Dialogue_ID,simpl_df$origin_text,simpl_df$lum,simpl_df$vividRGB)
}
```

Sample Test
```{r}
w = "marla"

word_lum_graph(subs_word_clean, query = w, choice = "Time",  flip = "N") 
word_RGB_graph(subs_word_clean, query = w, choice = "Time", correction = "medium", flip = "N") 
word_lum_RGB_scatter(subs_word_clean, query = w, choice = "Time", correction = "medium",size=8)
word_lum_RGB_scatter(subs_word_clean, query = w, choice = "Time", correction = "strong",size=8)
word_lum_RGB_scatter_smooth(subs_word_clean, query = w, choice = "Time", correction = "medium", size=2, span=1)
head(word_lum_RGB_scatter_data(subs_word_clean, query = w, choice = "Time"))
```

## 4 word_temp [Scatter]

get_temp function
```{r}
get_temp = function(r,g,b){
  hsl = as.hsv(rgb(r,g,b, maxColorValue = 255))
  temp = hsl[1]
  if (temp>180){
    temp = (360-temp)
  }
  return(temp)
}
```

main function
```{r}
word_temp_RGB_scatter = function(subs_word_clean,query,choice,correction,size){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  w_df$temp = 0
  
  for (i in 1:nrow(w_df)){
    w_df[i,]$temp = get_temp(w_df[i,]$R,w_df[i,]$G,w_df[i,]$B)
  }
  
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  #graph
  if (choice == "Time") {
    
    p <- ggplot(w_df, aes(x=Timecode_in, y = temp, color = Time))  +
      geom_point(size = size) 
    
    return(p  + ggtitle("Word Query, temp/RGB Scatter",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none") +
      geom_hline(yintercept=90) +
      coord_cartesian(ylim = c(0, 180)))
    
  }
  if (choice == "ID") {
    p <- ggplot(w_df, aes(x=as.numeric(Dialogue_ID), y = temp, color = Dialogue_ID))  +
      geom_point(size = size) 
    return(p  + ggtitle("Word Query, temp/RGB Scatter",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none") +
      geom_hline(yintercept=90) +
      coord_cartesian(ylim = c(0, 180))
      )
      
      
  }
}

##EXECUTE GRAPH

word_temp_RGB_scatter_smooth = function(subs_word_clean,query,choice,correction,size,span){
  
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c(correction))
  w_df$temp = 0
  
  for (i in 1:nrow(w_df)){
    w_df[i,]$temp = get_temp(w_df[i,]$R,w_df[i,]$G,w_df[i,]$B)
  }
  
  #for color matching
  simpl_df = w_df  %>% distinct
  
  
  #graph
  if (choice == "Time") {
    p <- ggplot(w_df, aes(x=Timecode_in, y = temp))  +
      geom_point(size = size) + geom_smooth(method = "loess",formula = 'y ~ x',color = "red",se = F , span = span)
    return(p  + ggtitle("Word Query, temp/RGB Scatter Geom_Smooth",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction, sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none") +
      geom_hline(yintercept=90) +
      coord_cartesian(ylim = c(0, 180))
      )
    
  }
  if (choice == "ID") {
    p <- ggplot(w_df, aes(x=as.numeric(Dialogue_ID), y = temp))  +
      geom_point(size = size) + geom_smooth(method = "loess",formula = 'y ~ x',color = "red",se = F ,span = span)
    return(p  + ggtitle("Word Query, temp/RGB Scatter Geom_Smooth",paste(moviename,"  |  '",w_df$word[1],"'  |  instances = ",w_df$n[1] , "  |  cor = ", correction,sep="")) + 
      scale_color_manual(values = simpl_df$vividRGB) + 
      theme(legend.position = "none"))
  }
}


##EXECUTE DATAFRAME

word_temp_RGB_scatter_data = function(subs_word_clean,query,choice){
  w_df = subs_word_clean %>% filter(word == query)
  w_df$Time = as.character(round_hms(w_df$Timecode_in, 1))
  w_df$h = 1 
  w_df$Dialogue_ID = str_pad(w_df$Dialogue_ID, 4, pad = "0")
  w_df$vividRGB = vividHex(w_df$hexRGB,c("light"))
  w_df$temp = 0
  
  for (i in 1:nrow(w_df)){
    w_df[i,]$temp = get_temp(w_df[i,]$R,w_df[i,]$G,w_df[i,]$B)
  }
  
  
  #for color matching
  simpl_df = w_df  %>% distinct
  #print dialogue data
  data.frame(simpl_df$Time,simpl_df$Dialogue_ID,simpl_df$origin_text,simpl_df$temp,simpl_df$vividRGB)
}
```

Sample Test
```{r}
w="marla"
word_temp_RGB_scatter(subs_word_clean, query = w, choice = "Time", correction = "ultra" , size=8)
word_temp_RGB_scatter_smooth(subs_word_clean, query = w, choice = "Time", correction = "medium", size=2, span=1)
head(word_temp_RGB_scatter_data(subs_word_clean, query = w, choice = "Time"))

```




